\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://joseph.ndigitalhorizon.com/}{\Large Joseph Naranjo}} & \faEnvelope\hspace{0.5em}Email :
  \href{mailto:dylan.naranjo@hotmail.com}{dylan.naranjo@hotmail.com}\\
  \href{https://joseph.ndigitalhorizon.com/}{https://joseph.ndigitalhorizon.com/} & \faPhone\hspace{0.5em}Phone : +14377775041 \\
  \href{https://github.com/DylanN25}{GitHub: @joseph-naranjo} & \faLinkedin \hspace{0.5em}LinkedIn : \href{https://www.linkedin.com/in/joseph-naranjo/}{@joseph-naranjo}
\end{tabular*}

%----------INTRODUCTION-----------------
\section{About Me}
Electronic Engineer specializing in AI architectures, multi-sensor data pipelines, and machine learning systems applied to industrial environments. Experienced in designing real-time data acquisition systems, training and deploying ML models using PyTorch and scikit-learn, and building scalable backends that support AI-driven decision-making. Proven ability to bridge physical hardware systems (PLCs, Modbus, IIoT) with production ML inference pipelines, a combination rare among AI/Data Engineering candidates.

%----------KEY ACHIEVEMENTS-----------------
\section{Key Achievements}
\resumeSubHeadingListStart
  \resumeSubItem{NASA Space Apps Challenge}{Global Finalist --- Top 45 Worldwide (2025)}
  \resumeSubItem{Published Author}{\href{http://www.revistasocialfronteriza.com/ojs/index.php/rev/article/view/603}{``Application of Neural Networks and Computer Vision for NFT Hydroponic Crop Control Systems''}}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
    {Micro1}{Palo Alto, CA (Remote)}
    {AI Training Specialist (Electronics \& EDA)}{Apr 2026 -- Present}
  \resumeItemListStart
    \resumeItem{Expert Model Evaluation}
      {Evaluating and fine-tuning Large Language Models (LLMs) on complex Electronic Design Automation (EDA) tasks, specifically focusing on circuit analysis and SPICE simulation accuracy.}
    \resumeItem{Circuit Simulation Validation}
      {Developing and executing test cases using \textbf{ngspice} to validate AI-generated netlists, ensuring theoretical correctness and adherence to electrical engineering principles.}
    \resumeItem{Technical Content Optimization}
      {Reviewing and optimizing AI-generated technical documentation for hardware-software integration, multi-sensor data synchronization, and industrial IoT architectures.}
    \resumeItem{EDA Workflow Automation}
      {Assessing AI capabilities for automated schematic-to-netlist conversion and analog circuit optimization, maintaining high standards for precision and reliability.}
  \resumeItemListEnd

  %--- Orillia ---
  \resumeSubheading
    {Orillia WoodWorking Inc.}{Orillia, ON}
    {Automation \& Systems Engineer}{Full-Time · On-Site · Aug 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Multi-Sensor Data Ingestion \& Pipeline Design}
      {Designed an industrial data acquisition system integrating PLCs and IoT gateways for continuous real-time telemetry across multiple machine sensors.}
    \resumeItem{High-Throughput Data Transmission}
      {Built real-time pipelines using Node-RED, routing sensor streams to redundant storage across Firebase and PostgreSQL with data integrity guarantees.}
    \resumeItem{Real-Time Monitoring \& KPI Computation}
      {Developed a live machine status monitoring system computing operational KPIs and downtime categories from live sensor feeds.}
    \resumeItem{Hardware-Software Integration}
      {Diagnosed and maintained electrical control systems (motors, VFDs, contactors) ensuring reliable, low-latency hardware-to-software data interfaces.}
    \resumeItem{Backend Architecture}
      {Built a PostgreSQL-based ERP integrated with the monitoring platform, supporting production workflows and operational data traceability.}
  \resumeItemListEnd

  %--- NDigital Horizon ---
  \resumeSubheading
    {NDigital Horizon}{Barrie, ON}
    {Founder \& Lead AI Solutions Architect}{Self-Employed · Jan 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Technology Consultancy}
      {Founded and operate a technology consultancy focused on AI automation and IIoT solutions for SMBs across Canada and Latin America.}
    \resumeItem{Audi-Conta}
      {Architected a tax automation platform that processes SRI XML invoices using AI (Vertex AI + Claude), reducing administrative processing time for SMB clients.}
    \resumeItem{DK Sport Arena}
      {Developed a booking and operations management system for DK Sport Arena, automating scheduling and client workflows.}
    \resumeItem{Cloud Architecture}
      {Architected a web stack combining Supabase (auth, PostgreSQL, real-time) with Firebase (FCM, analytics) and Cloudflare R2 for scalable AI-powered application deployments.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeSubItem{AI \& Machine Learning}
    {PyTorch, scikit-learn, Anomaly Detection, Predictive Maintenance, RAG Systems, Firestore Vector Search, Vertex AI, Embeddings, Claude API, Gemini API}
  \resumeSubItem{Data \& Pipelines}
    {Real-Time Data Processing, Multi-Sensor Ingestion, Data Synchronization, PostgreSQL, Firebase, Supabase, Apache Cassandra}
  \resumeSubItem{Programming}
    {Python, SQL, C++, Node-RED, REST APIs, Git, Docker}
  \resumeSubItem{Infrastructure}
    {Cloud (Google Cloud, Firebase), Firestore, Supabase, Cloudflare R2}
  \resumeSubItem{Hardware Integration}
    {PLCs, Modbus, IIoT, Sensor Data Acquisition, Electrical Panel Design, VFD \& Motor Control}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Georgian College}{Barrie, ON, CA}
    {Graduate Certificate - Artificial Intelligence: Architecture, Design, and Implementation}{}
  \resumeSubheading
    {Salesian Polytechnic University}{Quito, EC}
    {Bachelor of Engineering - Electronic Engineering}{}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubItem{\href{https://github.com/DylanN25/SmartDiagnosticsFailure}{Smart Diagnostics Failure | AI-Powered Anomaly Detection System}}
    {Developed an AI-powered system for industrial equipment failure detection using raw sensor data. Built and trained machine learning models in Python and PyTorch for anomaly detection and predictive analysis. Implemented a Modbus-based data acquisition layer and designed a scalable processing pipeline architected for both edge and cloud deployment.

    Tech: Python · PyTorch · Modbus · scikit-learn · Real-Time Data Pipeline}

  \resumeSubItem{Industrial Data Acquisition \& Monitoring System | IIoT Architecture}
    {Designed and deployed a production-ready real-time monitoring system for a manufacturing environment. Integrated industrial-grade hardware (PLCs, gateways) with a multi-layer data backend, enabling continuous sensor data ingestion, KPI computation, and operational visibility across the plant floor.

    Tech: Node-RED · PostgreSQL · Firebase · Docker · Industrial IoT · REST APIs}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------------
\section{Certifications}
\resumeSubHeadingListStart
  \resumeSubItem{Certifications}
    {AWS Academy Machine Learning  (2025) \\ Google Developers Event --- Participation Certificate (Toronto, 2025)}
\resumeSubHeadingListEnd

\end{document}
