\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://joseph.ndigitalhorizon.com/}{\Large Joseph Naranjo}} & \faEnvelope\hspace{0.5em}Email :
  \href{mailto:dylan.naranjo@hotmail.com}{dylan.naranjo@hotmail.com}\\
  \href{https://joseph.ndigitalhorizon.com/}{https://joseph.ndigitalhorizon.com/} & \faPhone\hspace{0.5em}Phone : +14377775041 \\
  \href{https://github.com/DylanN25}{GitHub: @joseph-naranjo} & \faLinkedin \hspace{0.5em}LinkedIn : \href{https://www.linkedin.com/in/joseph-naranjo/}{@joseph-naranjo}
\end{tabular*}

%----------INTRODUCTION-----------------
\section{About Me}
Electronic Engineer and Software Developer based in Barrie, Ontario, with production experience building full-stack systems for industrial and business environments. Specialized in backend architecture, database design, and integration of AI capabilities into real-world applications. Experienced shipping complete systems, from database schema to frontend, using PostgreSQL, Supabase, Next.js, and cloud infrastructure. 

%----------KEY ACHIEVEMENTS-----------------
\section{Key Achievements}
\resumeSubHeadingListStart
  \resumeSubItem{NASA Space Apps Challenge}{Global Finalist --- Top 45 Worldwide (2025)}
  \resumeSubItem{Published Author}{\href{http://www.revistasocialfronteriza.com/ojs/index.php/rev/article/view/603}{``Application of Neural Networks and Computer Vision for NFT Hydroponic Crop Control Systems''}}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

  %--- Orillia ---
  \resumeSubheading
    {Orillia WoodWorking Inc.}{Orillia, ON}
    {Automation \& Systems Engineer}{Full-Time · On-Site · Aug 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Canadian Work Experience}
      {Full-time, on-site engineering role within a Canadian manufacturing environment, direct experience with Ontario industrial operations, safety standards, and cross-functional team collaboration.}
    \resumeItem{ERP System Architecture}
      {Developed a PostgreSQL-based ERP covering purchase/sales orders, work orders, quotations, inventory management, and material tracking, integrated with the CMMS platform, tailored for custom manufacturing without fixed catalogs.}
    \resumeItem{CMMS Development}
      {Designed and built a full maintenance management system, machine documentation, scheduled tasks, real-time status monitoring, and KPI dashboards.}
    \resumeItem{IoT Backend Integration}
      {Built real-time data pipelines connecting industrial hardware (PLCs, gateways) to Firebase and PostgreSQL backends, ensuring data redundancy and availability.}
    \resumeItem{Database Design}
      {Designed multi-schema PostgreSQL databases with RLS, trigger functions, and automated backup workflows via GitHub Actions.}
  \resumeItemListEnd

  %--- NDigital Horizon ---
  \resumeSubheading
    {NDigital Horizon}{Barrie, ON}
    {Founder \& Lead AI Solutions Architect}{Self-Employed · Jan 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Technology Consultancy}
      {Founded and operate a technology consultancy focused on AI automation and IIoT solutions for SMBs across Canada and Latin America.}
    \resumeItem{Audi-Conta}
      {Architected a tax automation platform that processes SRI XML invoices using AI (Vertex AI + Claude), reducing administrative processing time for SMB clients.}
    \resumeItem{DK Sport Arena}
      {Developed a booking and operations management system for DK Sport Arena, automating scheduling and client workflows.}
    \resumeItem{Cloud Infrastructure}
      {Architected a multi-tenant web stack combining Supabase (auth, PostgreSQL, real-time), Firebase (FCM, analytics, App Hosting), and Cloudflare R2, optimizing infrastructure costs.}
  \resumeItemListEnd

%--- Micro1 ---
\resumeSubheading
    {Micro1}{Palo Alto, CA (Remote)}
    {AI Training Specialist (Electronics \& EDA)}{Apr 2026 -- Present}
  \resumeItemListStart
    \resumeItem{Expert Model Evaluation}
      {Evaluating and fine-tuning Large Language Models (LLMs) on complex Electronic Design Automation (EDA) tasks, specifically focusing on circuit analysis and SPICE simulation accuracy.}
    \resumeItem{Circuit Simulation Validation}
      {Developing and executing test cases using \textbf{ngspice} to validate AI-generated netlists, ensuring theoretical correctness and adherence to electrical engineering principles.}
    \resumeItem{Technical Content Optimization}
      {Reviewing and optimizing AI-generated technical documentation for hardware-software integration, multi-sensor data synchronization, and industrial IoT architectures.}
    \resumeItem{EDA Workflow Automation}
      {Assessing AI capabilities for automated schematic-to-netlist conversion and analog circuit optimization, maintaining high standards for precision and reliability.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Backend \& Databases}
    {PostgreSQL, Supabase, Firebase, REST APIs, Node-RED, SQL, Row-Level Security, Trigger Functions}
  \resumeSubItem{Frontend \& Full-Stack}
    {Next.js, React, TypeScript, HTML/CSS}
  \resumeSubItem{AI Integration}
    {Claude API, Vertex AI, Gemini API, RAG Systems}
  \resumeSubItem{Programming}
    {Python, JavaScript/TypeScript, SQL, C++, Matlab}
  \resumeSubItem{DevOps \& Infrastructure}
    {Docker, Git, GitHub Actions, Cloud (AWS, Google Cloud), Cloudflare R2}
  \resumeSubItem{Systems}
    {Industrial IoT, Modbus, PLCs, REST APIs}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Georgian College}{Barrie, ON, CA}
    {Graduate Certificate - Artificial Intelligence: Architecture, Design, and Implementation}{}
  \resumeSubheading
    {Salesian Polytechnic University}{Quito, EC}
    {Bachelor of Engineering - Electronic Engineering}{}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

  \resumeSubItem{ERP \& CMMS Platform | Integrated Manufacturing Operations System}
    {Designed and deployed a full-stack operations platform for a manufacturing plant, integrating a CMMS and ERP into a unified PostgreSQL backend. Supports purchase/sales orders, work orders, inventory management, and real-time machine monitoring, replacing manual workflows across production, maintenance, and procurement teams.

    Tech: PostgreSQL · Supabase · Next.js · Firebase · Docker · GitHub Actions · Row-Level Security}

  \resumeSubItem{Audi-Conta | AI Tax Automation Platform}
    {Built a SaaS platform for SMB clients that processes SRI XML invoices using AI (Vertex AI + Claude), automating tax document handling and reducing administrative overhead for small and medium businesses.

    Tech: Vertex AI · Claude API · PostgreSQL · Supabase · Next.js}

  \resumeSubItem{\href{https://github.com/DylanN25/SmartDiagnosticsFailure}{Smart Diagnostics Failure | AI-Powered Anomaly Detection System}}
    {Developed an AI-powered system for industrial equipment failure detection using raw sensor data. Built and trained machine learning models in Python and PyTorch for anomaly detection and predictive analysis. Implemented a Modbus-based data acquisition layer and designed a scalable processing pipeline architected for both edge and cloud deployment.

    Tech: Python · PyTorch · Modbus · scikit-learn · Real-Time Data Pipeline}

\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------------
\section{Certifications}
\resumeSubHeadingListStart
  \resumeSubItem{Certifications}
    {AWS Academy Machine Learning (2025) \\ Google Developers Event --- Participation Certificate (Toronto, 2025)}
\resumeSubHeadingListEnd

\end{document}
