\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://joseph.ndigitalhorizon.com/}{\Large Joseph Naranjo}} & \faEnvelope\hspace{0.5em}Email :
  \href{mailto:dylan.naranjo@hotmail.com}{dylan.naranjo@hotmail.com}\\
  \href{https://joseph.ndigitalhorizon.com/}{https://joseph.ndigitalhorizon.com/} & \faPhone\hspace{0.5em}Phone : +14377775041 \\
  \href{https://github.com/DylanN25}{GitHub: @joseph-naranjo} & \faLinkedin \hspace{0.5em}LinkedIn : \href{https://www.linkedin.com/in/joseph-naranjo/}{@joseph-naranjo}
\end{tabular*}

%----------INTRODUCTION-----------------
\section{About Me}
Electronic Engineer with hands-on experience in industrial environments in Canada, specializing in electrical systems, automation, and the integration of hardware-software architectures. Experienced in the design of electrical panels, maintenance and diagnostics of industrial machinery, and deployment of IoT-based data acquisition systems. Focused on building reliable infrastructure that bridges physical industrial environments with scalable software systems.

%----------KEY ACHIEVEMENTS-----------------
\section{Key Achievements}
\resumeSubHeadingListStart
  \resumeSubItem{NASA Space Apps Challenge}{Global Finalist --- Top 45 Worldwide (2025)}
  \resumeSubItem{Published Author}{\href{http://www.revistasocialfronteriza.com/ojs/index.php/rev/article/view/603}{``Application of Neural Networks and Computer Vision for NFT Hydroponic Crop Control Systems''}}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

  %--- Micro1 ---
\resumeSubheading
    {Micro1}{Palo Alto, CA (Remote)}
    {AI Training Specialist (Electronics \& EDA)}{Apr 2026 -- Present}
  \resumeItemListStart
    \resumeItem{Expert Model Evaluation}
      {Evaluating and fine-tuning Large Language Models (LLMs) on complex Electronic Design Automation (EDA) tasks, specifically focusing on circuit analysis and SPICE simulation accuracy.}
    \resumeItem{Circuit Simulation Validation}
      {Developing and executing test cases using \textbf{ngspice} to validate AI-generated netlists, ensuring theoretical correctness and adherence to electrical engineering principles.}
    \resumeItem{Technical Content Optimization}
      {Reviewing and optimizing AI-generated technical documentation for hardware-software integration, multi-sensor data synchronization, and industrial IoT architectures.}
    \resumeItem{EDA Workflow Automation}
      {Assessing AI capabilities for automated schematic-to-netlist conversion and analog circuit optimization, maintaining high standards for precision and reliability.}
  \resumeItemListEnd

%--- Orillia Woodworking Inc. ---
\resumeSubheading
  {Orillia WoodWorking Inc.}{Orillia, ON}
  {Automation \& Systems Engineer}{Full-Time · Aug 2024 -- Present}
\resumeItemListStart
  \resumeItem{Industrial Maintenance \& MTTR Optimization}
    {Performed preventive and corrective maintenance on motors, VFDs, and control systems; **reduced machine downtime by 10\%** and improved **Mean Time To Repair (MTTR) by 50\%** by implementing a historical fault-tracking system for faster diagnostics.}
  \resumeItem{IoT \& Data Acquisition Architecture}
    {Designed and deployed an IoT-integrated electrical panel with PLCs and Node-RED, enabling real-time telemetry and redundant storage (PostgreSQL/Firebase) for **100\% data traceability** of critical machine assets.}
  \resumeItem{ERP \& Administrative Efficiency}
    {Architected a custom PostgreSQL-based ERP, **reducing administrative processing time by 40\%** through automated material tracking, sales orders, and inventory synchronization for custom manufacturing workflows.}
  \resumeItem{Operational Accuracy}
    {Eliminated inventory inconsistencies and minimized manual entry errors by developing a unified CMMS/ERP platform, providing a **single source of truth** for production and maintenance KPIs.}
  \resumeItem{Canadian Standards Compliance}
    {Ensured all electrical and software implementations met Ontario industrial safety standards while collaborating with cross-functional teams to optimize plant-floor operations.}
\resumeItemListEnd

  %--- NDigital Horizon ---
  \resumeSubheading
    {NDigital Horizon}{Barrie, ON}
    {Founder \& Lead AI Solutions Architect}{Self-Employed · Jan 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Technology Consultancy}
      {Founded and operate a technology consultancy focused on AI automation and IIoT solutions for SMBs across Canada and Latin America.}
    \resumeItem{Audi-Conta}
      {Architected a tax automation platform that processes SRI XML invoices using AI (Vertex AI + Claude), reducing administrative processing time for SMB clients.}
    \resumeItem{DK Sport Arena}
      {Developed a booking and operations management system for DK Sport Arena, automating scheduling and client workflows.}
    \resumeItem{Loxone Official Partner}
      {Official Loxone Partner, certified in professional building automation and smart home systems. Currently offering home and commercial automation services through NDigital Horizon's dedicated automation division (\href{https://automation.ndigitalhorizon.com}{automation.ndigitalhorizon.com}).}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Engineering \& Automation}
    {Industrial Systems, Electrical Panel Design, PLCs, VFDs, Contactors, Motor Control, Modbus Communication, Preventive \& Corrective Maintenance, IIoT, Automation and Control}
  \resumeSubItem{Programming \& Systems}
    {Python, SQL, Node-RED, Thingsboard, PostgreSQL, Firebase, Git, REST APIs, Matlab}
  \resumeSubItem{AI \& Data (Applied)}
    {Anomaly Detection, KPI Modeling, Machine Usage Analytics, Data Pipelines}
  \resumeSubItem{Infrastructure}
    {Docker, Cloud Services (AWS, Google), Industrial Networking}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Georgian College}{Barrie, ON, CA}
    {Graduate Certificate - Artificial Intelligence: Architecture, Design, and Implementation}{}
  \resumeSubheading
    {Salesian Polytechnic University}{Quito, EC}
    {Bachelor of Engineering - Electronic Engineering}{}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeSubItem{Industrial Data Acquisition \& Monitoring System | IIoT Architecture}
    {Designed and deployed a production-ready real-time monitoring system for a manufacturing environment. Integrated industrial-grade hardware (PLCs, gateways) with a multi-layer data backend, enabling continuous sensor data ingestion, KPI computation, and operational visibility across the plant floor.

    Tech: Node-RED · PostgreSQL · Firebase · Docker · Industrial IoT · REST APIs}

  \resumeSubItem{\href{https://github.com/DylanN25/SmartDiagnosticsFailure}{Smart Diagnostics Failure | AI-Powered Anomaly Detection System}}
    {Developed an AI-powered system for industrial equipment failure detection using raw sensor data. Built and trained machine learning models in Python and PyTorch for anomaly detection and predictive analysis. Implemented a Modbus-based data acquisition layer and designed a scalable processing pipeline architected for both edge and cloud deployment.

    Tech: Python · PyTorch · Modbus · scikit-learn · Real-Time Data Pipeline}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------------
\section{Certifications}
\resumeSubHeadingListStart
  \resumeSubItem{Certifications}
    {AWS Academy Machine Learning (2025) \\ Google Developers Event --- Participation Certificate (Toronto, 2025)}
\resumeSubHeadingListEnd

\end{document}
  \resumeSubItem{Certifications}
    {AWS Academy Machine Learning Foundations (2025) \\ Google Developers Event --- Participation Certificate (Toronto, 2025)}
\resumeSubHeadingListEnd

\end{document}
